% Acknowledgements

\pdfbookmark[1]{Acknowledgements}{Acknowledgements} % Bookmark name visible in a PDF viewer

%----------------------------------------------------------------------------------------

\begingroup

\let\clearpage\relax
\let\cleardoublepage\relax
\let\cleardoublepage\relax

\chapter*{Acknowledgements} % Acknowledgements section text

I would like to express my sincere gratitude to  Dr. Ritaban Dutta who offered the greatest support that I could ever expect from any supervisor, both in terms of research guidance and financial support. \\
\newline
I'd like to show my appreciation for the support I received from my family and friends as I was often working late and unable to attend on many occasions. 
I'd like to thank my colleagues and fellow vacation scholarship students for the help in the process of completing the work in the thesis. I'd also like to thank the CSIRO Computational Informatics, Hobart and the Tasmanian node of the Australian Centre for Broadband Innovation for providing the full support for my individual project.\\
\newline
My sincere thanks also goes to Mr. Jeremy Smith, the university course coordinator, and Dr. Jon Kim, my university supervisor, who offered me the opportunity to extend the time for completing the thesis and provided helpful feedback during the mid-term review.\\
\newline
Lastly, even though I did not have the opportunity to collaborate with them, I would like to appreciate the work other people had done so that the data are made available for the work of the thesis. The cosmic ray sensor data was made available through the CosmOz Australian soil moisture monitoring network funded by CSIRO and deployed by Aaron Hawdon and Rex Keen of CSIRO Land and Water, Townsville, Australia. Soil samples for sensor calibration were collected by Bill Cotching of Tasmanian Institute of Agriculture. Data were delivered
through CSIRO data service system developed by Peter Taylor. I would like to thank Peter Briggs and Simon Lovell for providing access to the AWAP database and SILO database. I would also like to acknowledge the
use of FIRMS data and imagery from the Land Atmosphere Near-real time Capability for EOS (LANCE) system operated by the NASA/GSFC/Earth Science Data and Information System (ESDIS) with funding provided by
NASA/HQ.
\endgroup